---
title: ''
output:
  word_document:
    reference_docx: /conf/LIST_analytics/West Hub/02 - Scaled Up Work/RMarkdown/Locality
      Profiles/Master RMarkdown Document & Render Code/Locality_Profiles_Report_Template.docx
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(kableExtra.auto_format = FALSE)

# Line below for testing only
# LOCALITY <-  "Skye, Lochalsh and West Ross"
# LOCALITY <- "Falkirk West"
# LOCALITY <- "Stirling City with the Eastern Villages Bridge of Allan and Dunblane"
# LOCALITY <- "Ayr North and Former Coalfield Communities"
# LOCALITY <- "Helensburgh and Lomond"
# LOCALITY <- "City of Dunfermline"
# LOCALITY <- "Inverclyde East"
# LOCALITY <- "East Dunbartonshire West"

#lp_path <- "/conf/LIST_analytics/West Dunbartonshire/Locality Profiles Combined/"

source(here("Master RMarkdown Document & Render Code/Global Script.R"))

source(here("Unscheduled Care/2. Unscheduled Care outputs.R"))

x <- 1 # object for figure numbers
y <- 1 # object for table numbers
```

## Hospital and Community Care

\newline

**Summary**

**For the most recent time periods available, `r locality_list[1]` had:**

-   **`r latest_emergency_adm_loc1[1]`** emergency hospital admissions per 100,000 population, compared to `r scot_emergency_adm1` in Scotland.

-   **`r latest_bed_days_loc1[1]`** unscheduled acute specialty bed days per 100,000 population, compared to `r scot_bed_days1` in Scotland.

-   **`r latest_ae_att_loc1[1]`** A&E attendances per 100,000 population, compared to `r scot_ae_att1` in Scotland.

-   **`r latest_dd_loc1[1]`** delayed discharge bed days per 100,000 population aged over 65, compared to `r scot_dd1` in Scotland.

-   **`r latest_falls_loc1[1]`** emergency hospital admissions from falls per 100,000 population aged over 65, compared to `r scot_falls1` in Scotland.

-   **`r latest_read_loc1[1]`** emergency readmissions (28 day) per 1,000 discharges, compared to `r scot_read` in Scotland.

-   **`r latest_ppa_loc[[1]]$formatted_data[2]`** potentially preventable hospital admissions per 100,000 population, compared to `r scot_ppa$formatted_data[2]` in Scotland.

**For the most recent time periods available, `r locality_list[2]` had:**

-   **`r latest_emergency_adm_loc1[2]`** emergency hospital admissions per 100,000 population, compared to `r scot_emergency_adm1` in Scotland.

-   **`r latest_bed_days_loc1[2]`** unscheduled acute specialty bed days per 100,000 population, compared to `r scot_bed_days1` in Scotland.

-   **`r latest_ae_att_loc1[2]`** A&E attendances per 100,000 population, compared to `r scot_ae_att1` in Scotland.

-   **`r latest_dd_loc1[2]`** delayed discharge bed days per 100,000 population aged over 65, compared to `r scot_dd1` in Scotland.

-   **`r latest_falls_loc1[2]`** emergency hospital admissions from falls per 100,000 population aged over 65, compared to `r scot_falls1` in Scotland.

-   **`r latest_read_loc1[2]`** emergency readmissions (28 day) per 1,000 discharges, compared to `r scot_read` in Scotland.

-   **`r latest_ppa_loc[[2]]$formatted_data[2]`** potentially preventable hospital admissions per 100,000 population, compared to `r scot_ppa$formatted_data[2]` in Scotland.

##### Page break

### Emergency Admissions

Figure `r x` presents the emergency admissions rate per 100,000 population in the `r locality_list[1]` and `r locality_list[2]` localities from `r min_year_ea` to `r max_year_ea`.

As presented in Figure `r x`, the emergency admissions rate in the **`r locality_list[1]` locality** for `r max_year_ea` is `r latest_emergency_adm_loc1[1]`, `r get_article(percent_rate_change[1])` `r percent_rate_change[1]`% `r word_change_rate[1]` since `r min_year_ea`. The emergency admissions rate in the **`r locality_list[2]` locality** for `r max_year_ea` is `r latest_emergency_adm_loc1[2]`, `r get_article(percent_rate_change[2])` `r percent_rate_change[2]`% `r word_change_rate[2]` since `r min_year_ea`. 

The `r HSCP` HSCP rate is `r hscp_emergency_adm1`, `r get_article(hscp_rate_change)` `r hscp_rate_change`% `r word_change_hscp` since `r min_year_ea`. The `r HB` health board rate is `r hscp_emergency_adm1` in `r max_year_ea`, `r get_article(hb_rate_change)` `r hb_rate_change`% `r word_change_hb` since `r min_year_ea` and the Scotland rate is `r scot_emergency_adm1`, `r get_article(scot_rate_change)` `r scot_rate_change`% `r word_change_scot` since `r min_year_ea`.

#### Figure `r x`: Emergency admissions by geographical area

\newline

```{r echo = FALSE, fig.width = 9, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
EAs_loc_ts

x <- x + 1
```

Figure `r x` presents the emergency admissions rate per 100,000 population in the **`r locality_list[1]` locality** from `r min_ea_age[1]` to `r max_ea_age[1]` by age group.

As presented in Figure `r x`, the highest emergency admissions rate for the `r locality_list[1]` locality in `r max_ea_age[1]` is `r latest_ea_max_age1[1]` per 100,000 population for the `r age_group_max_ea[1]` age group with a percentage `r max_word_change_ea[1]` of `r max_rate_change_ea[1]`% since `r min_ea_age[1]`. The lowest emergency admissions rate for `r locality_list[1]` in `r max_ea_age[1]` is `r latest_ea_min_age1[1]` per 100,000 population for the `r age_group_min_ea[1]` age group with a percentage `r min_word_change_ea[1]` of `r min_rate_change_ea[1]`% since `r min_ea_age[1]`.

#### Figure `r x`: Emergency admissions by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE,  fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population split by age group."}
EAs_age_ts[[1]]

x <- x + 1
```

Figure `r x` presents the emergency admissions rate per 100,000 population in the **`r locality_list[2]` locality** from `r min_ea_age[2]` to `r max_ea_age[2]` by age group.

The highest emergency admissions rate for the `r locality_list[2]` locality in `r max_ea_age[2]` is `r latest_ea_max_age1[2]` per 100,000 population for the `r age_group_max_ea[2]` age group with a percentage `r max_word_change_ea[2]` of `r max_rate_change_ea[2]`% since `r min_ea_age[2]`. The lowest emergency admissions rate for `r locality_list[2]` in `r max_ea_age[2]` is `r latest_ea_min_age1[2]` per 100,000 population for the `r age_group_min_ea[2]` age group with a percentage `r min_word_change_ea[2]` of `r min_rate_change_ea[2]`% since `r min_ea_age[2]`.

#### Figure `r x`: Emergency admissions by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE,  fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population split by age group."}
EAs_age_ts[[2]]

x <- x + 1
```

##### Page break

### Unscheduled Acute Bed Days

Figure `r x` presents the unscheduled bed days rate per 100,000 population in the `r locality_list[1]` and `r locality_list[2]` localities from `r min_year_ubd` to `r max_year_ubd`.

As presented in Figure `r x`, the unscheduled bed days rate in the `r locality_list[1]` locality for `r max_year_ubd` is `r latest_bed_days_loc1[1]`, `r get_article(rate_change_ubd[1])` `r rate_change_ubd[1]`% `r word_change_ubd[1]` since `r min_year_ubd`. The unscheduled bed days rate in the `r locality_list[2]` locality for `r max_year_ubd` is `r latest_bed_days_loc1[2]`, `r get_article(rate_change_ubd[2])` `r rate_change_ubd[2]`% `r word_change_ubd[2]` since `r min_year_ubd`.

The `r HSCP` HSCP rate is `r hscp_bed_days1`, `r get_article(hscp_rate_ubd)` `r hscp_rate_ubd`% `r hscp_change_ubd` since `r min_year_ubd`. The `r HB` health board rate for `r max_year_ubd` is `r hb_bed_days1`, `r get_article(hb_rate_change_ubd)` `r hb_rate_change_ubd`% `r word_change_hb_ubd` since `r min_year_ubd` and the Scotland rate is `r scot_bed_days1`, `r get_article(scot_rate_ubd)` `r scot_rate_ubd`% `r scot_change_ubd` since `r min_year_ubd`.

#### Figure `r x`: Unscheduled acute bed days by geographical area

\newline

```{r echo = FALSE, fig.width = 9, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for unscheduled acute bed days per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
BDs_loc_ts

x <- x + 1
```

Figure `r x` presents the unscheduled bed days rate per 100,000 population in the **`r locality_list[1]` locality** from `r min_ubd_age[1]` to `r max_ubd_age[1]` by age group.

As presented in Figure `r x`, the highest unscheduled bed days rate for the **`r locality_list[1]` locality** in `r max_ubd_age[1]` is `r latest_ubd_max_age1[1]` bed days per 100,000 population for the `r age_group_max_ubd[1]` age group with a percentage `r max_word_change_ubd[1]` of `r max_rate_change_ubd[1]`% since `r min_ubd_age[1]`. The lowest unscheduled bed days rate for `r locality_list[1]` in `r max_ubd_age[1]` is `r latest_ubd_min_age1[1]` bed days per 100,000 population for the `r age_group_min_ubd[1]` age group with a percentage `r min_word_change_ubd[1]` of `r min_rate_change_ubd[1]`% since `r min_ubd_age[1]`.

#### Figure `r x`: Unscheduled acute bed days by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population split by age group."}
BDs_age_ts[[1]]

x <- x + 1
```

Figure `r x` presents the unscheduled bed days rate per 100,000 population in the **`r locality_list[2]` locality** from `r min_ubd_age[2]` to `r max_ubd_age[2]` by age group.

As presented in Figure `r x`, the highest unscheduled bed days rate for the **`r locality_list[2]` locality** in `r max_ubd_age[2]` is `r latest_ubd_max_age1[2]` bed days per 100,000 population for the `r age_group_max_ubd[2]` age group with a percentage `r max_word_change_ubd[2]` of `r max_rate_change_ubd[2]`% since `r min_ubd_age[2]`. The lowest unscheduled bed days rate for `r locality_list[2]` in `r max_ubd_age[2]` is `r latest_ubd_min_age1[2]` bed days per 100,000 population for the `r age_group_min_ubd[2]` age group with a percentage `r min_word_change_ubd[2]` of `r min_rate_change_ubd[2]`% since `r min_ubd_age[2]`.

#### Figure `r x`: Unscheduled acute bed days by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population split by age group."}
BDs_age_ts[[2]]

x <- x + 1
```

##### Page break

### A&E Attendances

Figure `r x` presents the A&E attendance rate per 100,000 population in the `r locality_list[1]` and `r locality_list[2]` localities from `r min_year_ae_area` to `r max_year_ae_area`.

As presented in Figure `r x`, the A&E attendance rate per 100,000 in the **`r locality_list[1]` locality** for `r max_year_ae_area` is `r latest_ae_att_loc1[1]`, `r get_article(percent_rate_change_ae_areas[1])` `r percent_rate_change_ae_areas[1]`% `r word_change_rate_ae_areas[1]` since `r min_year_ae_area`. The A&E attendance rate per 100,000 in the **`r locality_list[2]` locality** for `r max_year_ae_area` is `r latest_ae_att_loc1[2]`, `r get_article(percent_rate_change_ae_areas[2])` `r percent_rate_change_ae_areas[2]`% `r word_change_rate_ae_areas[2]` since `r min_year_ae_area`.

The `r HSCP` HSCP rate is `r hscp_ae_att1`, `r get_article(percent_rate_change_ae_areas_hscp)` `r percent_rate_change_ae_areas_hscp`% `r word_change_rate_ae_areas_hscp` since `r min_year_ae_area`. The `r HB` health board rate for `r max_year_ae_area` is `r hb_ae1`, `r get_article(hb_rate_change_ae)` `r hb_rate_change_ae`% `r word_change_hb_ae` since `r min_year_ae_area` and the Scotland rate is `r scot_ae_att1`, `r get_article(percent_rate_change_ae_areas_scot)` `r percent_rate_change_ae_areas_scot`% `r word_change_rate_ae_areas_scot` since `r min_year_ae_area`.

#### Figure `r x`: A&E attendances by geographical area

\newline

```{r echo = FALSE, fig.width = 9, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for A&E attendancess per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
AandE_loc_ts

x <- x + 1
```

Figure `r x` presents the A&E attendance rate per 100,000 population in the `r locality_list[1]` locality from `r min_year_ae_area` to `r max_year_ae_area` by age group.

As presented in Figure `r x`, the highest A&E attendance rate for the `r locality_list[1]` locality in `r max_year_ae_age[1]` is `r latest_ae_att_loc1_age[1]` per 100,000 population for the `r age_group_max[1]` age group with a percentage `r word_change_rate_ae_age[1]` of `r percent_rate_change_ae_age[1]`% since `r min_year_ae_age[1]`. The lowest A&E attendance rate for `r locality_list[1]` in `r max_year_ae_age[1]` is `r latest_ae_att_loc1_age_min[1]` per 100,000 population for the `r age_group_min[1]` age group with a percentage `r word_change_rate_ae_age2[1]` of `r percent_rate_change_ae_age2[1]`% since `r min_year_ae_age[1]`.

#### Figure `r x`: A&E attendances by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for A&E attendancess per 100,000 population split by age group."}
AandE_age_ts[[1]]

x <- x + 1
```

Figure `r x` presents the A&E attendance rate per 100,000 population in the `r locality_list[2]` locality from `r min_year_ae_area` to `r max_year_ae_area` by age group.

As presented in Figure `r x`, the highest A&E attendance rate for the `r locality_list[2]` locality in `r max_year_ae_age[2]` is `r latest_ae_att_loc1_age[2]` per 100,000 population for the `r age_group_max[2]` age group with a percentage `r word_change_rate_ae_age[2]` of `r percent_rate_change_ae_age[2]`% since `r min_year_ae_age[2]`. The lowest A&E attendance rate for `r locality_list[2]` in `r max_year_ae_age[2]` is `r latest_ae_att_loc1_age_min[2]` per 100,000 population for the `r age_group_min[2]` age group with a percentage `r word_change_rate_ae_age2[2]` of `r percent_rate_change_ae_age2[2]`% since `r min_year_ae_age[2]`.

#### Figure `r x`: A&E attendances by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for A&E attendancess per 100,000 population split by age group."}
AandE_age_ts[[2]]

x <- x + 1
```

##### Page break

### Emergency Readmissions (28 days)

Figure `r x` presents the emergency readmission (28 days) rate per 1,000 discharges in the `r locality_list[1]` and `r locality_list[2]` localities from `r min_year_re_area` to `r max_year_re_area`.

As presented in Figure `r x`, the emergency readmission (28 days) rate per 1,000 discharges in the **`r locality_list[1]` locality** for `r max_year_re_area` is `r latest_read_loc1[1]`, `r get_article(percent_rate_change_re_area[1])` `r percent_rate_change_re_area[1]`% `r word_change_rate_re_area[1]` since `r min_year_re_area`. The emergency readmission (28 days) rate per 1,000 discharges in the **`r locality_list[2]` locality** for `r max_year_re_area` is `r latest_read_loc1[2]`, `r get_article(percent_rate_change_re_area[2])` `r percent_rate_change_re_area[2]`% `r word_change_rate_re_area[2]` since `r min_year_re_area`.

The `r HSCP` HSCP rate is `r hscp_read`, `r get_article(percent_rate_change_re_area_hscp)` `r percent_rate_change_re_area_hscp`% `r word_change_rate_re_area_hscp` since `r min_year_re_area`. The `r HB` health board rate for `r max_year_re_area` is `r hb_read1`, `r get_article(hb_rate_change_read)` `r hb_rate_change_read`% `r word_change_hb_read` since `r min_year_re_area` and the Scotland rate is `r scot_read`, `r get_article(percent_rate_change_re_area_scot)` `r percent_rate_change_re_area_scot`% `r word_change_rate_re_area_scot` since `r min_year_re_area`.

#### Figure `r x`: Emergency readmissions (28 days) by geographical area

\newline

```{r echo = FALSE, fig.width = 9, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency readmissions per 1,000 discharges split by geographical area."}
read_loc_ts

x <- x + 1
```

Figure `r x` presents the emergency readmission (28 days) rate per 1,000 discharges in the **`r locality_list[1]` locality** from `r min_year_re_age[1]` to `r max_year_re_age[1]` by age group.

As presented in Figure `r x`, the highest emergency readmission (28 days) rate for the `r locality_list[1]` locality in `r max_year_re_age[1]` is `r latest_re_max_age_data[1]` per 1,000 discharges for the `r latest_re_max_age_group[1]` age group with a percentage `r word_change_rate_re_age[1]` of `r percent_rate_change_re_age[1]`% since `r min_year_re_age[1]`. The lowest emergency readmission (28 days) rate for the `r locality_list[1]` locality in `r max_year_re_age[1]` is `r latest_re_min_age_data[1]` per 1,000 discharges for the `r latest_re_min_age_group[1]` age group with a percentage `r word_change_rate_re_age_min[1]` of `r percent_rate_change_re_age_min[1]`% since `r min_year_re_age[1]`.

#### Figure `r x`: Emergency readmissions (28 days) by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency readmissions per 1,000 discharges split by age group."}
read_age_ts[[1]]

x <- x + 1
```

Figure `r x` presents the emergency readmission (28 days) rate per 1,000 discharges in the **`r locality_list[2]` locality** from `r min_year_re_age[2]` to `r max_year_re_age[2]` by age group.

As presented in Figure `r x`, the highest emergency readmission (28 days) rate for the `r locality_list[2]` locality in `r max_year_re_age[2]` is `r latest_re_max_age_data[2]` per 1,000 discharges for the `r latest_re_max_age_group[2]` age group with a percentage `r word_change_rate_re_age[2]` of `r percent_rate_change_re_age[2]`% since `r min_year_re_age[2]`. The lowest emergency readmission (28 days) rate for the `r locality_list[2]` locality in `r max_year_re_age[2]` is `r latest_re_min_age_data[2]` per 1,000 discharges for the `r latest_re_min_age_group[2]` age group with a percentage `r word_change_rate_re_age_min[2]` of `r percent_rate_change_re_age_min[2]`% since `r min_year_re_age[2]`.

#### Figure `r x`: Emergency readmissions (28 days) by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency readmissions per 1,000 discharges split by age group."}
read_age_ts[[2]]

x <- x + 1
```

##### Page break

### Delayed Discharge Bed Days

Figure `r x` presents the number of delayed discharge bed days per 100,000 population aged over 65+ in the `r locality_list[1]` and `r locality_list[2]` locality from `r min_year_dd` to `r max_year_dd`.

As presented in Figure `r x`, the number of delayed discharge bed days per 100,000 population aged over 65+ in the **`r locality_list[1]` locality** for `r max_year_dd` is `r latest_dd_loc1[1]`, `r get_article(percent_rate_change_dd_loc[1])` `r percent_rate_change_dd_loc[1]`% `r word_change_rate_dd_loc[1]` since `r min_year_dd`. The number of delayed discharge bed days per 100,000 population aged over 65+ in the **`r locality_list[2]` locality** for `r max_year_dd` is `r latest_dd_loc1[2]`, `r get_article(percent_rate_change_dd_loc[2])` `r percent_rate_change_dd_loc[2]`% `r word_change_rate_dd_loc[2]` since `r min_year_dd`.

The `r HSCP` HSCP rate is `r hscp_dd1`, `r get_article(percent_rate_change_dd_hscp)` `r percent_rate_change_dd_hscp`% `r word_change_rate_dd_hscp` since `r min_year_dd`. The `r HB` health board rate for `r max_year_dd` is `r hb_dd1`, `r get_article(hb_rate_change_dd)` `r hb_rate_change_dd`% `r word_change_hb_dd` since `r min_year_dd` and the Scotland rate is `r scot_dd1`, `r get_article(percent_rate_change_dd_scot)` `r percent_rate_change_dd_scot`% `r  word_change_rate_dd_scot` since `r min_year_dd`.

#### Figure `r x`: Delayed discharge bed days in the population aged 65+ by geographical area

\newline

```{r echo = FALSE, fig.width = 9, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for delayed discharge beddays per 100,000 population aged 65+ split by geographical area."}
DD_loc_ts

x <- x + 1
```

### Emergency admissions from a fall

Figure `r x` presents the emergency admissions from falls rate per 100,000 population aged 65 and over in the `r locality_list[1]` and `r locality_list[2]` localities from `r min_year_falls` to `r max_year_falls`.

As presented in Figure `r x`, the emergency admissions from falls rate per 100,000 population aged over 65+ in the **`r locality_list[1]` locality** for `r max_year_falls` is `r latest_falls_loc1[1]`, `r get_article(percent_rate_change_falls_loc[1])` `r percent_rate_change_falls_loc[1]`% `r word_change_rate_falls_loc[1]` since `r min_year_falls`. The emergency admissions from falls rate per 100,000 population aged over 65+ in the **`r locality_list[2]` locality** for `r max_year_falls` is `r latest_falls_loc1[2]`, `r get_article(percent_rate_change_falls_loc[2])` `r percent_rate_change_falls_loc[2]`% `r word_change_rate_falls_loc[2]` since `r min_year_falls`.

The `r HSCP` HSCP rate is `r hscp_falls1`, `r get_article(percent_rate_change_falls_hscp)` `r percent_rate_change_falls_hscp`% `r word_change_rate_falls_hscp` since `r min_year_falls`. The `r HB` health board rate for `r max_year_falls` is `r hb_falls1`, `r get_article(hb_rate_change_falls)` `r hb_rate_change_falls`% `r word_change_hb_falls` since `r min_year_falls` and the Scotland rate is `r scot_falls1`, `r get_article(percent_rate_change_falls_scot)` `r percent_rate_change_falls_scot`% `r  word_change_rate_falls_scot` since `r min_year_falls`.

#### Figure `r x`: Falls in the population aged 65+ by geographical area

\newline

```{r echo = FALSE, fig.width = 9, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency admissions from a fall per 100,000 population aged 65+ split by geographical area."}
Falls_loc_ts

x <- x + 1
```

##### Page break

### Potentially Preventable Admissions (PPAs)

Information on the conditions included in Potentially Preventable Admissions (PPA)s is available in Appendix 3. Figure `r x` presents the PPA rate per 100,000 population in the `r locality_list[1]` and `r locality_list[2]` localities from `r min_year_ppa_areas` to `r max_year_ppa_areas`.

In `r max_fy`, **`r latest_ppa_65plus[1]`%** of PPAs in **`r locality_list[1]`** were amongst those aged 65 and over, and **`r latest_ppa_under65[1]`%** were amongst those aged under 65. The rate per 100,000 population for PPAs in the **`r locality_list[1]` locality** for `r max_year_ppa_areas` is `r latest_ppa_loc[1]$formatted_data[2]`, `r get_article(ppa_diff[1])` `r ppa_diff[1]`% `r ppa_word_change[1]` since `r latest_ppa_loc[1]$financial_year[1]`.

In `r max_fy`, **`r latest_ppa_65plus[2]`%** of PPAs in **`r locality_list[2]`** were amongst those aged 65 and over, and **`r latest_ppa_under65[2]`%** were amongst those aged under 65. The rate per 100,000 population for PPAs in the **`r locality_list[2]` locality** for `r max_year_ppa_areas` is `r latest_ppa_loc[2]$formatted_data[2]`, `r get_article(ppa_diff[2])` `r ppa_diff[2]`% `r ppa_word_change[2]` since `r latest_ppa_loc[2]$financial_year[1]`. 

The `r HSCP` HSCP rate is `r hscp_ppa$data[2]`, `r get_article(ppa_diff_hscp)` `r ppa_diff_hscp`% `r ppa_word_change_hscp` since `r latest_ppa_loc$financial_year[1]`. The `r HB` health board rate for `r hb_ppa$financial_year[2]` is `r hb_ppa$formatted_data[2]`, `r get_article(diff_hb_ppa)` `r diff_hb_ppa`% `r word_change_hb_ppa` since `r hb_ppa$financial_year[]` and the Scotland rate is `r scot_ppa$formatted_data[2]`, `r get_article(diff_scot_ppa)` `r diff_scot_ppa`% `r  word_change_scot_ppa` since `r hb_ppa$financial_year[1]`.

#### Figure `r x`: Potentially Preventable Admissions (PPAs) by geographical area

\newline

```{r echo = FALSE, fig.width = 9, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for potentially preventable admissions per 100,000 population split by geographical area."}
ppa_loc_ts

x <- x + 1
```

\newline

##### Page break

## Hospital Care (Mental Health Speciality)

\newline

**Summary**

This section looks at mental health-related unscheduled care indicators. 

For the most recent time period available, **`r locality_list[1]`** had:

-   **`r psych_hosp_latest[1]`** psychiatric patient hospitalisations per 100,000, compared to `r scot_psych_hosp[1]$measure[2]` in Scotland^4^.
-   **`r latest_bed_days_mh_loc1[1]`** unscheduled mental health specialty bed days per 100,000, compared to `r scot_bed_days_mh1` in Scotland.

For the most recent time period available, **`r locality_list[2]`** had:

-   **`r psych_hosp_latest[2]`** psychiatric patient hospitalisations per 100,000, compared to `r scot_psych_hosp[2]$measure[2]` in Scotland^4^.
-   **`r latest_bed_days_mh_loc1[2]`** unscheduled mental health specialty bed days per 100,000, compared to `r scot_bed_days_mh1` in Scotland.

\newline

### Psychiatric patient hospitalisations

Figure `r x` presents the psychiatric patient hospitalisation 3-year aggregate rate per 100,000 population in the `r locality_list[1]` and `r locality_list[2]` localities from `r loc_psych_hosp[1]$period_short[1]` to `r loc_psych_hosp[1]$period_short[2]`.

As presented in Figure `r x`, the 3-year aggregate psychiatric patient hospitalisation rate per 100,000 population in the **`r locality_list[1]` locality** for `r loc_psych_hosp[1]$period_short[2]` is `r loc_psych_hosp[1]$measure[2]`, `r get_article(diff_loc_psych[1])` `r diff_loc_psych[1]`% `r word_change_loc_psych[1]` since `r loc_psych_hosp[1]$period_short[1]`. The 3-year aggregate psychiatric patient hospitalisation rate per 100,000 population in the **`r locality_list[2]` locality** for `r loc_psych_hosp[2]$period_short[2]` is `r loc_psych_hosp[2]$measure[2]`, `r get_article(diff_loc_psych[2])` `r diff_loc_psych[2]`% `r word_change_loc_psych[2]` since `r loc_psych_hosp[2]$period_short[1]`.

The `r HSCP` HSCP rate is `r hscp_psych_hosp$measure[2]`, `r get_article(diff_hscp_psych)` `r diff_hscp_psych`% `r word_change_hscp_psych` since `r loc_psych_hosp$period_short[1]`. The `r HB` health board the 3-year aggregate rate for `r loc_psych_hosp$period_short[2]` is `r hb_psych_hosp$measure[2]`, `r get_article(diff_hb_psych)` `r diff_hb_psych`% `r word_change_hb_psych` since `r loc_psych_hosp$period_short[1]` and the Scotland the 3-year aggregate rate is `r scot_psych_hosp$measure[2]`, `r get_article(diff_scot_psych)` `r diff_scot_psych`% `r word_change_scot_psych` since `r loc_psych_hosp$period_short[1]`.

#### Figure `r x`: Psychiatric patient hospitalisations by geographical area

\newline

```{r echo = FALSE, fig.width = 9, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing ten-year time trends grouped into 3 year aggregates for psychiatric patient hospitalisations per 100,000 population split by geographical area."}
psych_hosp_time_trend

x <- x + 1
```

##### Page break

### Unscheduled Mental Health Specialty Bed Days

Figure `r x` presents the unscheduled mental health bed days rate per 100,000 population in the `r locality_list[1]` and `r locality_list[2]` localities from `r min_year_bd_mh_areas` to `r max_year_bd_mh_areas`.

As presented in Figure `r x`, the unscheduled mental health bed days rate per 100,000 population in the **`r locality_list[1]` locality** for `r max_year_bd_mh_areas` is `r latest_bed_days_mh_loc1[1]`, `r get_article(loc_rate_change_beds_mh[1])` `r loc_rate_change_beds_mh[1]`% `r loc_word_change_beds_mh[1]` since `r min_year_bd_mh_areas`. The unscheduled mental health bed days rate per 100,000 population in the **`r locality_list[2]` locality** for `r max_year_bd_mh_areas` is `r latest_bed_days_mh_loc1[2]`, `r get_article(loc_rate_change_beds_mh[2])` `r loc_rate_change_beds_mh[2]`% `r loc_word_change_beds_mh[2]` since `r min_year_bd_mh_areas`.

The `r HSCP` HSCP rate is `r hscp_bed_days_mh1`, `r get_article(hscp_rate_change_beds_mh)` `r hscp_rate_change_beds_mh`% `r hscp_word_change_beds_mh` since `r min_year_bd_mh_areas`. The `r HB` health board rate for `r max_year_bd_mh_areas` is `r hb_mh_beddays1`, `r get_article(hb_rate_change_mh)` `r hb_rate_change_mh`% `r word_change_hb_mh` since `r  min_year_bd_mh_areas` and the Scotland rate is `r scot_bed_days_mh1`, `r get_article(scot_rate_change_beds_mh)` `r scot_rate_change_beds_mh`% `r  scot_word_change_beds_mh` since `r min_year_bd_mh_areas`.

#### Figure `r x`: Unscheduled mental health specialty bed days by geographical area

\newline

```{r echo = FALSE, fig.width = 9, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for uncscheduled mental health specialty bed days per 100,000 population split by geographical area."}
BDMH_loc_ts

x <- x + 1
```

Figure `r x` presents the unscheduled mental health bed days rate per 100,000 in the `r locality_list[1]` locality from `r min_year_bd_mh_age[1]` to `r max_year_bd_mh_age[1]` by age group.

As presented in Figure `r x`, the highest unscheduled mental health bed days rate for the `r locality_list[1]` locality in `r max_year_bd_mh_age[1]` is `r latest_bd_mh_max_age1[1]` per 100,000 population for the `r age_group_max_mh[1]` age group with a percentage `r max_word_change_beds_mh[1]` of `r max_rate_change_beds_mh[1]`% since `r min_year_bd_mh_age[1]`. The lowest unscheduled mental health bed days rate for the `r locality_list[1]` locality in `r max_year_bd_mh_age[1]` is `r latest_bd_mh_min_age1[1]` per 100,000 population for the `r age_group_min_mh[1]` age group with a percentage `r min_word_change_beds_mh[1]` of `r min_rate_change_beds_mh[1]`% since `r min_year_bd_mh_age1[1]`.

#### Figure `r x`: Unscheduled mental health specialty bed days by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing six-year time trends for uncscheduled mental health specialty bed days per 100,000 population split by geographical area."}
BDMH_age_ts[[1]]

x <- x + 1
```

Figure `r x` presents the unscheduled mental health bed days rate per 100,000 in the `r locality_list[2]` locality from `r min_year_bd_mh_age[2]` to `r max_year_bd_mh_age[2]` by age group.

As presented in Figure `r x`, the highest unscheduled mental health bed days rate for the `r locality_list[2]` locality in `r max_year_bd_mh_age[2]` is `r latest_bd_mh_max_age1[2]` per 100,000 population for the `r age_group_max_mh[2]` age group with a percentage `r max_word_change_beds_mh[2]` of `r max_rate_change_beds_mh[2]`% since `r min_year_bd_mh_age[2]`. The lowest unscheduled mental health bed days rate for the `r locality_list[2]` locality in `r max_year_bd_mh_age[2]` is `r latest_bd_mh_min_age1[2]` per 100,000 population for the `r age_group_min_mh[2]` age group with a percentage `r min_word_change_beds_mh[2]` of `r min_rate_change_beds_mh[2]`% since `r min_year_bd_mh_age1[2]`.

#### Figure `r x`: Unscheduled mental health specialty bed days by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing six-year time trends for uncscheduled mental health specialty bed days per 100,000 population split by geographical area."}
BDMH_age_ts[[2]]

x <- x + 1
```