---
title: ''
output:
  word_document:
    fig_caption: false
    reference_docx: "/conf/LIST_analytics/West Hub/02 - Scaled Up Work/RMarkdown/Locality
      Profiles/Master RMarkdown Document & Render Code/Locality_Profiles_Report_Template.docx"
  html_document:
    fig_caption: false
    df_print: paged
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(kableExtra.auto_format = FALSE)

x <- 1 # object for figure numbers
y <- 1 # object for table numbers
```

```{r testing_setup, include = FALSE}
# Line below for testing only
# LOCALITY <- "Falkirk West"
# LOCALITY <- "Stirling City with the Eastern Villages Bridge of Allan and Dunblane"
# LOCALITY <- "Helensburgh and Lomond"
# LOCALITY <- "City of Dunfermline"
# LOCALITY <- "Skye, Lochalsh and West Ross"
# LOCALITY <- "Ayr North and Former Coalfield Communities"

#source("Master RMarkdown Document & Render Code/Global Script.R")

#lp_path <- "/conf/LIST_analytics/West Dunbartonshire/Locality Profiles Combined/"
```

```{r produce_data, include = FALSE}

source(here::here("Master RMarkdown Document & Render Code", "Locality Profiles parameter values.R"))
source(here::here("Lifestyle & Risk Factors/2. Lifestyle & Risk Factors Outputs.R"))
```

## Lifestyle and Risk Factors

\newline

**Summary**

Mental and physical well-being has close ties with people's lifestyles and behaviours. Financial security, employment and location are influences that often have a bearing on these choices. Issues can develop when alcohol, smoking or drug use shape lives. This section provides data on drug-related hospital admissions, alcohol-related hospital admissions, alcohol-specific deaths and bowel screening uptake, to give an overview of some of the lifestyles and behaviours for `r locality_list[1]` and `r locality_list[2]` localities. These can give an idea of quality of life and prosperity.

For the most recent time period available^3^, **`r locality_list[1]`** had:

-   **`r format_number_for_text(alcohol_hosp_latest[[1]])`** alcohol-related hospital admissions per 100,000 age-sex standardised population. This is `r alcohol_hosp_diff_scot[[1]]` than Scotland (`r  format_number_for_text(scot_alcohol_hosp)` admissions per 100,000)^4^.
-   **`r format_number_for_text(alcohol_deaths_latest[[1]])`** alcohol-specific deaths per 100,000 age-sex standardised population. This is `r alcohol_deaths_diff_scot[[1]]` than Scotland (`r  format_number_for_text(scot_alcohol_deaths)` deaths per 100,000)^4^.
-   **`r format_number_for_text(drug_hosp_latest[[1]])`** drug-related hospital admissions per 100,000 age-sex standardised population. This is `r drug_hosp_diff_scot[[1]]` than Scotland (`r format_number_for_text(scot_drug_hosp)` admissions per 100,000)^4^.
-   **`r format_number_for_text(bowel_screening_latest[[1]])`%** uptake of bowel screening among the eligible population, compared to `r format_number_for_text(scot_bowel_screening)`% in Scotland.

\newline

For the most recent time period available^3^, **`r locality_list[2]`** had:

-   **`r format_number_for_text(alcohol_hosp_latest[[2]])`** alcohol-related hospital admissions per 100,000 age-sex standardised population. This is `r alcohol_hosp_diff_scot[[2]]` than Scotland (`r  format_number_for_text(scot_alcohol_hosp)` admissions per 100,000)^4^.
-   **`r format_number_for_text(alcohol_deaths_latest[[2]])`** alcohol-specific deaths per 100,000 age-sex standardised population. This is `r alcohol_deaths_diff_scot[[2]]` than Scotland (`r  format_number_for_text(scot_alcohol_deaths)` deaths per 100,000)^4^.
-   **`r format_number_for_text(drug_hosp_latest[[2]])`** drug-related hospital admissions per 100,000 age-sex standardised population. This is `r drug_hosp_diff_scot[[2]]` than Scotland (`r format_number_for_text(scot_drug_hosp)` admissions per 100,000)^4^.
-   **`r format_number_for_text(bowel_screening_latest[[2]])`%** uptake of bowel screening among the eligible population, compared to `r format_number_for_text(scot_bowel_screening)`% in Scotland.

\newline

### Alcohol-related Hospital Admissions

In `r latest_period_alcohol_hosp`, the rate of alcohol-related admissions was **`r format_number_for_text(alcohol_hosp_latest[[1]])`** per 100,000 age-sex standardised population in **`r locality_list[1]`**. This is `r get_article(alcohol_hosp_change[[1]])` `r format_number_for_text(alcohol_hosp_change[[1]])`% `r alcohol_hosp_change_word[[1]]` overall since `r earliest_period_alcohol_hosp`. 

In `r latest_period_alcohol_hosp`, the rate of alcohol-related admissions was **`r format_number_for_text(alcohol_hosp_latest[[2]])`** per 100,000 age-sex standardised population in **`r locality_list[2]`**. This is `r get_article(alcohol_hosp_change[[2]])` `r format_number_for_text(alcohol_hosp_change[[2]])`% `r alcohol_hosp_change_word[[2]]` overall since `r earliest_period_alcohol_hosp`. 

Figure `r x` shows a trend of alcohol-related hospital admissions for `r locality_list[1]` and `r locality_list[2]` localities compared with Scotland, `r HSCP` HSCP and `r HB` from financial year `r earliest_period_alcohol_hosp` to `r latest_period_alcohol_hosp`.

#### Figure `r x`: Alcohol-related hospital admission rates by area and over time.

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing 10-year time trends for alcohol-related hospital admissions per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
alcohol_hosp_time_trend

x <- x + 1
```

Figure `r x` compares different areas, including the other localities in `r HSCP`, for the latest financial year. This bar chart shows that in `r latest_period_alcohol_hosp`, **`r locality_list[1]` locality** had a `r alcohol_hosp_diff_scot[[1]]` alcohol-related hospital admissions rate compared to Scotland (`r format_number_for_text(alcohol_hosp_latest[[1]])` and `r  format_number_for_text(scot_alcohol_hosp)` admissions respectively). In `r latest_period_alcohol_hosp`, **`r locality_list[2]` locality** had a `r alcohol_hosp_diff_scot[[2]]` alcohol-related hospital admissions rate compared to Scotland (`r format_number_for_text(alcohol_hosp_latest[[2]])` and `r  format_number_for_text(scot_alcohol_hosp)` admissions respectively).


##### Page break

#### Figure `r x`: Alcohol-related hospital admissions by area for the latest time period.

\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4.8, warning = FALSE, fig.cap = "A bar graph showing alcohol-related hospital admissions per 100,000 population for Locality, HSCP, Health Board and all Scotland and all other localities in the HSCP for the most recent financial year."}
alcohol_hosp_bar

x <- x + 1
```

\newline

### Alcohol-Specific Deaths

Data on alcohol-specific deaths is available as 5-year aggregates. In `r locality_list[1]`, the latest rate of alcohol-specific deaths was **`r format_number_for_text(alcohol_deaths_latest[[1]])`** deaths per 100,000 age-sex standardised population. This is `r format_number_for_text(alcohol_deaths_change[[1]])`% `r alcohol_deaths_change_word[[1]]` than the rate in `r earliest_period_alcohol_deaths`. Figure `r x + 1` also shows that the locality has a `r alcohol_deaths_diff_scot[[1]]` alcohol-specific death rate compared to Scotland overall (`r  format_number_for_text(scot_alcohol_deaths)` deaths per 100,000). 

In `r locality_list[2]`, the latest rate of alcohol-specific deaths was **`r format_number_for_text(alcohol_deaths_latest[[2]])`** deaths per 100,000 age-sex standardised population. This is `r format_number_for_text(alcohol_deaths_change[[2]])`% `r alcohol_deaths_change_word[[2]]` than the rate in `r earliest_period_alcohol_deaths`. Figure `r x + 1` also shows that the locality has a `r alcohol_deaths_diff_scot[[2]]` alcohol-specific death rate compared to Scotland overall (`r  format_number_for_text(scot_alcohol_deaths)` deaths per 100,000).

#### Figure `r x`: Alcohol-specific deaths by area and over time.

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing 10-year time trends for 5 year aggregate rates of alcohol-specific deaths per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
alcohol_deaths_time_trend

x <- x + 1
```

#### Figure `r x`: Alcohol-specific deaths by area for the latest time period available.

\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4.5, warning = FALSE, fig.cap =  "A bar graph showing the 5 year aggregate rate of alcohol-specific deaths per 100,000 population for Locality, HSCP, Health Board and all Scotland and all other localities in the HSCP for the most recent time period."}
alcohol_deaths_bar

x <- x + 1
```

\newline

### Drug-related Hospital Admissions

A trend of the change in drug-related hospital admissions for the locality and comparable areas is shown in Figure `r x` from `r earliest_period_drug_hosp_trend` onward.

There were **`r format_number_for_text(drug_hosp_latest[[1]])`** drug-related hospital admissions per 100,000 age-sex standardised population^4^ in the **`r locality_list[1]` locality** in the time period `r latest_period_drug_hosp` (3-year financial year aggregate). This is `r get_article(drug_hosp_change[[1]])` `r format_number_for_text(drug_hosp_change[[1]])`% `r drug_hosp_change_word[[1]]` since `r earliest_period_drug_hosp`. 

There were **`r format_number_for_text(drug_hosp_latest[[2]])`** drug-related hospital admissions per 100,000 age-sex standardised population^4^ in the **`r locality_list[2]` locality** in the time period `r latest_period_drug_hosp` (3-year financial year aggregate). This is `r get_article(drug_hosp_change[[2]])` `r format_number_for_text(drug_hosp_change[[2]])`% `r drug_hosp_change_word[[2]]` since `r earliest_period_drug_hosp`. 

A comparison of areas at the most recent time period (`r latest_period_drug_hosp` aggregated financial years) is available in Figure `r x + 1`. This shows the **`r locality_list[1]` locality** has a `r drug_hosp_diff_scot[[1]]` rate of drug-related hospital admissions than Scotland (`r format_number_for_text(scot_drug_hosp)` admissions per 100,000). **`r locality_list[2]` locality** has a `r drug_hosp_diff_scot[[2]]` rate of drug-related hospital admissions than Scotland (`r format_number_for_text(scot_drug_hosp)` admissions per 100,000). 

#### Figure `r x`: Drug-related hospital admission rates by area and over time.

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing time trends for 3 year aggregate rates of drug-related hospital admissions per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
drug_hosp_time_trend

x <- x + 1
```

##### Page break

#### Figure `r x`: Drug-related hospital admission rates by area for the latest time period available.

```{r echo = FALSE, fig.width = 8, fig.height = 4.8, warning = FALSE, fig.cap= "A bar graph showing the 3 year rate of drug-related hospital admissions per 100,000 population for Locality, HSCP, Health Board and all Scotland and all other localities in the HSCP for the most recent time period."}
drug_hosp_bar

x <- x + 1
```

\newline

### Bowel Screening Uptake

Bowel screening is offered every two years to eligible men and women aged between 50-74 years old. Eligible people are posted a test kit which is completed at home. Since 1st April 2013, those aged 75 and over can also self-refer and opt into screening.

A trend of the percentage uptake of bowel screening among the eligible population is shown for `r locality_list[1]` and `r locality_list[2]` and comparable areas. Data is presented as 3-year aggregates. 

The `r latest_period_bowel_screening` uptake rate for `r locality_list[1]` is **`r format_number_for_text(bowel_screening_latest[[1]])`%**. This is `r get_article(bowel_screening_change[[1]])` `r format_number_for_text(bowel_screening_change[[1]])`% `r bowel_screening_change_word[[1]]` since `r earliest_period_bowel_screening`. As can be seen in Figure `r x + 1`, in the latest estimate, the uptake in `r locality_list[1]` was `r bowel_screening_diff_scot[[1]]` than the uptake in Scotland overall (`r format_number_for_text(scot_bowel_screening)`%).

The `r latest_period_bowel_screening` uptake rate for `r locality_list[2]` is **`r format_number_for_text(bowel_screening_latest[[2]])`%**. This is `r get_article(bowel_screening_change[[2]])` `r format_number_for_text(bowel_screening_change[[2]])`% `r bowel_screening_change_word[[2]]` since `r earliest_period_bowel_screening`. As can be seen in Figure `r x + 1`, in the latest estimate, the uptake in `r locality_list[2]` was `r bowel_screening_diff_scot[[2]]` than the uptake in Scotland overall (`r format_number_for_text(scot_bowel_screening)`%).

##### Page break

#### Figure `r x`: Bowel screening uptake for eligible men and women, by area and over time.

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing time trends for 3 year aggregate rates for bowel screening uptake by percentage of eligible population for Locality, HSCP, Health Board and all Scotland."}
bowel_screening_time_trend

x <- x + 1
```

#### Figure `r x`: Bowel screening uptake by area for the latest time period available.

\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4.8, warning = FALSE, fig.cap = "A bar graph showing the most recent 3 year aggregate rates for bowel screening uptake by percentage of eligible population for Locality, HSCP, Health Board and all Scotland and for all localities within the HSCP."}
bowel_screening_bar

x <- x + 1
```
