---
title: ''
output:
  word_document:
    reference_docx: "/conf/LIST_analytics/West Hub/02 - Scaled Up Work/RMarkdown/Locality
      Profiles/Master RMarkdown Document & Render Code/Locality_Profiles_Report_Template.docx"
  html_document:
    df_print: paged
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(kableExtra.auto_format = FALSE)

# Line below for testing only
# LOCALITY <- "Falkirk West"
# LOCALITY <- "Stirling City with the Eastern Villages Bridge of Allan and Dunblane"
# LOCALITY <- "Helensburgh and Lomond"
# LOCALITY <- "City of Dunfermline"
# LOCALITY <- "Skye, Lochalsh and West Ross"
# LOCALITY <- "Ayr North and Former Coalfield Communities"

source(here("Households","Households Code.R"))

x <- 1 # object for figure numbers
y <- 1 # object for table numbers
```

##### Page break

## Households

###Summary:

\newline

**For the most recent time periods available, `r locality_list[1]` Locality had:**

 - **`r n_houses[[1]]`** dwellings, of which: **`r perc_occupied[[1]]`%** were occupied and **`r perc_second_homes[[1]]`%** were second homes.
 - **`r perc_single_discount[[1]]`%** of dwellers received a single occupant council tax discount, and **`r perc_exempt[[1]]`%** were exempt from council tax entirely.
 - **`r perc_houses_AC[[1]]`%** of houses were within council tax bands A to C, and **`r perc_houses_FH[[1]]`%** were in bands F to H.

\newline

**For the most recent time periods available, `r locality_list[2]` Locality had:**

 - **`r n_houses[[2]]`** dwellings, of which: **`r perc_occupied[[2]]`%** were occupied and **`r perc_second_homes[[2]]`%** were second homes.
 - **`r perc_single_discount[[2]]`%** of dwellers received a single occupant council tax discount, and **`r perc_exempt[[2]]`%** were exempt from council tax entirely.
 - **`r perc_houses_AC[[2]]`%** of houses were within council tax bands A to C, and **`r perc_houses_FH[[2]]`%** were in bands F to H.

\newline

#### `r locality_list[1]`

The graph below shows the number of dwellings in **`r locality_list[1]`** from `r min(household_sheet_titles)` to `r max(household_sheet_titles)`.

####Figure `r x`: Number of dwellings time trend in `r locality_list[1]`.
\newline

```{r echo = FALSE, fig.width = 7, fig.height = 3, warning = FALSE}
houses_ts[[1]]

x <- x + 1
```

#### `r locality_list[2]`

The graph below shows the number of dwellings in **`r locality_list[2]`** from `r min(household_sheet_titles)` to `r max(household_sheet_titles)`.

####Figure `r x`: Number of dwellings time trend in `r locality_list[2]`.
\newline

```{r echo = FALSE, fig.width = 7, fig.height = 3, warning = FALSE}
houses_ts[[2]]

x <- x + 1
```

#### Dwellings
##### `r locality_list[1]`

Of the total number of dwellings in `r max(household_sheet_titles)`, `r perc_single_discount[[1]]`% (`r n_single_discount[[1]]` households) were occupied by an individual receiving a single occupant council tax discount. Furthermore, `r perc_exempt[[1]]`% (`r n_exempt[[1]]` households) were occupied and exempt from council tax. 

There were `r n_second_homes[[1]]` dwellings classed as a second home in `r max(household_sheet_titles)`, these dwellings made up `r perc_second_homes[[1]]`% of the households in `r locality_list[[1]]`.

#####Page break

####Table `r y`: Breakdown of dwelling types by year for `r locality_list[1]` locality.
\newline
										
```{r echo = FALSE}
knitr::kable(house_table[[1]],
  col.names = c(
    "**Year**", "**Total Dwellings**", "**Occupied Dwellings**",
    "**Vacant Dwellings**", "**Single Occupant Tax Discount**", "**Council Tax Exempt Dwellings**", "**Second Homes**"
  ),
  align = c("l", "r", "r", "r", "r", "r", "r")
)

y <- y + 1
```

\newline
##### `r locality_list[2]`
Of the total number of dwellings in `r max(household_sheet_titles)`, `r perc_single_discount[[2]]`% (`r n_single_discount[[2]]` households) were occupied by an individual receiving a single occupant council tax discount. Furthermore, `r perc_exempt[[2]]`% (`r n_exempt[[2]]` households) were occupied and exempt from council tax. 

There were `r n_second_homes[[2]]` dwellings classed as a second home in `r max(household_sheet_titles)`, these dwellings made up `r perc_second_homes[[2]]`% of the households in `r locality_list[[2]]`.

\newline
										
```{r echo = FALSE}
knitr::kable(house_table[[2]],
  col.names = c(
    "**Year**", "**Total Dwellings**", "**Occupied Dwellings**",
    "**Vacant Dwellings**", "**Single Occupant Tax Discount**", "**Council Tax Exempt Dwellings**", "**Second Homes**"
  ),
  align = c("l", "r", "r", "r", "r", "r", "r")
)

y <- y + 1
```


The proportion of households within each council tax band are displayed in the chart below, figures are shown in Table `r y`.

####Figure `r x`: Breakdown of households by council tax band for `r locality_list[1]` in `r max(household_sheet_titles)`.
\newline

```{r echo = FALSE, fig.width = 7, fig.height = 2, warning = FALSE}
ctb_plot[[1]]

x <- x + 1
```

####Table `r y`: Percentage of households by council tax band for `r locality_list[2]` in `r max(household_sheet_titles)`.
\newline

```{r echo = FALSE}
knitr::kable(ctb_table,
  col.names = c(
    "**Tax Band**", "**A**", "**B**", "**C**",
    "**D**", "**E**", "**F**", "**G**", "**H**"
  ),
  align = c("l", rep("r", 8))
)

y <- y + 1
```
